\bf Service Chain Placement in SDNs \thanks{Research supported in part by Network Programming (Neptune) Consortium, Israel.}

### 2018-01-07 src/chain.tex
fix

\begin{abstract}
We study the allocation problem of a compound request for a
\emph{service chain} in a software defined network that supports
network function virtualization.
%
Given a network that contains servers with limited processing power
and of links with limited bandwidth, a service chain is a sequence of
virtual network functions (VNFs) that service a certain flow request
in the network.
%
The allocation of a service chain consists of routing and VNF
placement, namely each VNF from the sequence is placed in a server
along a path.  It is feasible if each server can handle the VNFs that
are assigned to it, and if each link on the path can carry the flow
that is assigned to it.
%
A request for service is composed of a source and a destination in the
network, an upper bound on the total latency, and a specification in
the form of a directed acyclic graph (DAG) of VNFs that provides all
service chains that are considered valid for this request.
%
In addition, each pair of server and VNF is associated with a cost for
placing the VNF in the server.  Given a request, the goal is to find a
valid service chain of minimum total cost that respects the latency
constraint or to identify that such a service chain does not exist.

@@

In this paper we consider an SDN network that employs
NVF~\cite{SDN-NFV15}.  Such networks attracted a lot of attention in
the networking community, especially from a systems point of view
(see, e.g.,~\cite{GVPGKDA14,HVSBFTF15}).  Several papers also consider
the algorithmic aspects of such networks but mainly present heuristics
(see, e.g,~\cite{SBMPKSF14}).  For more details see~\cite{ERS16} and
references therein.

@@

We study the allocation problem of a compound flow request for a
service chain in a software-defined network that supports NFV, where
the goal is to find an optimal placement with respect to the current
available resources from the point of view of the network (i.e., the
ISP).
%
More specifically, we consider the case where the network already
contains previous resource allocations.  Therefore, we are given a
(physical) network that contains servers with limited (residual)
processing power and of links with limited (residual) bandwidth.
%
A request for service is composed of a source and a destination in the
network, an upper bound on the total latency, and a specification of
all service chains that are considered valid for this request.  As
in~\cite{EMP16}, the specification is represented by a DAG whose
vertices are VNFs.
%
The allocation of a service chain consists of routing and VNF
placement.  That is, each VNF from the sequence is placed in a server
along a path, and it is feasible if each server can handle the VNFs
that are assigned to it, and if each link on the path can carry the
flow that is assigned to it.  Moreover each link causes a delay, and
the service chain placement should also comply with a global bound on
the total latency.
%
Each pair of server and VNF is associated with a cost for placing the
network function in the server.  This cost measures compatibility of a
VNF to a server (e.g., infinite costs means ``incompatible'').  Given
a request, the goal is to find a feasible service chain of minimum
total cost or to identify that a valid service chain does not exist.

@@

@@

\begin{figure}
\begin{center}
\input{fig-or2}
\end{center}
\caption{
A undirected graph with its block marked in a dashed, green lines.
In this instance, using the trivial approach the orientation phase takes 16! iterations,
while using the second approach we only need 3! iterations.
\label{fig:or2}
}
\end{figure}   
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{FPT Algorithm for General Networks}
We now propose an FPT algorithm for general networks that is similar to the randomized 
algorithm from Section~\ref{sec:general}.
Our FPT algorithm runs in $O(k! \cdot (A + O))$ where $k$ is the number of neighborly
vertices in the graph, $A$ is the time required to find a solution on a DAG,
and $O$ is the time required to orient the graph given a permutation on the neighborly
vertices, as discussed above.
The algorithm executes the FPTAS for DAGs given in Theorem~\ref{thm:fptas}
once for any orientation results from any of the $k!$ possible permutations and
returns the best solution.
The following theorem follows immediately.

>>>>

\begin{abstract}
We study the allocation problem of a compound request for a
\emph{service chain} in a software defined network that supports
network function virtualization.
%
Given a network that contains servers with limited processing power
and links with limited bandwidth, a service chain is a sequence of
virtual network functions (VNFs) that serve a certain flow request
in the network.
%
The allocation of a service chain consists of routing and VNF
placement, namely each VNF from the sequence is placed in a server
along a path.  It is feasible if each server can handle the VNFs that
are assigned to it, and if each link on the path can carry the flow
that is assigned to it.
%
A request for service is composed of a source and a destination in the
network, an upper bound on the total latency, and a specification in
the form of a directed acyclic graph (DAG) of VNFs that provides all
service chains that are considered valid for this request.
%
In addition, each pair of server and VNF is associated with a cost for
placing the VNF in the server.  Given a request, the goal is to find a
valid service chain of minimum total cost that respects the latency
constraint or to identify that such a service chain does not exist.

@@

In this paper we consider an SDN network that employs
NVF~\cite{SDN-NFV15}.  Such networks attracted a lot of attention in
the networking community, especially from a systems point of view
(see, e.g.,~\cite{GVPGKDA14,HVSBFTF15}).  Several papers also consider
the algorithmic aspects of such networks but mainly present heuristics
(see, e.g,~\cite{soule2014merlin}).  
For more details see~\cite{ERS16} and references therein.

@@

We study the allocation problem of a compound flow request for a
service chain in a software-defined network that supports NFV, where
the goal is to find an optimal placement with respect to the current
available resources from the point of view of the network (i.e., the
ISP).
%
More specifically, we consider the case where the network already
contains previous resource allocations.  Therefore, we are given a
(physical) network that contains servers with limited (residual)
processing power and links with limited (residual) bandwidth.
%
A request for service is composed of a source and a destination in the
network, an upper bound on the total latency, and a specification of
all service chains that are considered valid for this request.  As
in~\cite{EMP16}, the specification is represented by a DAG whose
vertices are VNFs.
%
The allocation of a service chain consists of routing and VNF
placement.  That is, each VNF from the sequence is placed in a server
along a path, and it is feasible if each server can handle the VNFs
that are assigned to it, and if each link on the path can carry the
flow that is assigned to it.  Moreover each link causes a delay, and
the service chain placement should also comply with a global bound on
the total latency.
%
Each pair of server and VNF is associated with a cost for placing the
network function in the server.  This cost measures compatibility of a
VNF to a server (e.g., infinite costs means ``incompatible'').  Given
a request, the goal is to find a feasible service chain of minimum
total cost or to identify that a valid service chain does not exist.

@@

\section{FPT Algorithms for General Networks}
We now propose an FPT algorithm for general networks that is similar to the randomized 
algorithm from Section~\ref{sec:general}.
Our FPT algorithm runs in $O(k! \cdot (A + O))$ where $k$ is the number of neighborly
vertices in the graph, $A$ is the time required to find a solution on a DAG,
and $O$ is the time required to orient the graph given a permutation on the neighborly
vertices, as discussed above.
The algorithm executes the FPTAS for DAGs given in Theorem~\ref{thm:fptas}
once for any orientation results from any of the $k!$ possible permutations and
returns the best solution.
The following theorem follows immediately.

@@

\begin{figure}
\begin{center}
\input{fig-or2}
\end{center}
\caption{
A undirected graph with its block marked in a dashed, green lines.
In this instance, using the trivial approach the orientation phase takes 16! iterations,
while using the second approach we only need 3! iterations.
\label{fig:or2}
}
\end{figure}
